Grip strength, mating success, and immune and energy costs in a population sample of US women and men: a registered report

### 2024-08-14 paper.qmd
Merged

```{r}
source('functions.R')
source('pilot_analysis.R')
source('sexspecificmodels.R')
source('stage2_analysis.R')
source('compare.R')

@@

>>>>

```{r}
source('functions.R')
source('pilot_analysis.R')
source('sexspecificmodels.R')
source('stage2_analysis.R')
source('compare.R')
source('combinedGH.R')

@@

## Combined G and H series data (2011-2014)

:::{#sfig-matingGH}

```{r}
#| fig-width: 12
#| fig-height: 9
plot_strengthGH
```

Strength coefficients from models of mating fit on combined data.
:::

:::{#sfig-effectsGH}

```{r}
#| fig-width: 12
#| fig-height: 12
plot_effects_lifetime_GH / plot_effects_partners_GH + plot_layout(axes = 'collect', guides = 'collect')
```

Strength coefficients effects plots of mating success models fit on combined data.
:::

:::{#sfig-immunityGH}

```{r}
#| fig-width: 11
#| fig-height: 6
plot_immune_strength_GH
```

Strength coefficients from immunity models fit on combined data.
:::

:::{#sfig-intakeGH}

```{r}
#| fig-width: 9
#| fig-height: 6
plot_intake_strength_GH
```

Strength coefficients from energy and protein intake models fit on combined data.
:::
